A general and efficient representation of Ancestral Recombination Graphs

### 2022-08-25 paper.tex
Move discussion of ARGs into precision section

\section*{Precision of recombination information}

@@

For example, \citep{deng2021distribution} state that
``[the ARG] provides
all the information about the genealogical history of a sample,
including the locations of recombination events.''

@@

@@

\section*{Differences in reconstructed ARGs}
ARGs inferred by different methods vary greatly in their properties.
To illustrate this, we examine the inferences made by four
recent methods on the classical \citet{kreitman1983nucleotide}.
\emph{Drosophila melanogaster} dataset.

@@

@@

Note that all four methods produce output which can be represented in the
succinct tree sequence format, and which is consistent with our definition of
an ARG as a data structure. The ARGs produced by \texttt{KwARG} and
\texttt{ARGweaver} contain more nodes to record the recombination events
(corresponding to Figure 4 stage `B'), while the ARGs output by
\texttt{tsinfer} and \texttt{Relate} being, in essence, simplified (roughly
corresponding to Figure 4 stages `C' and 'D', respectively).

\section*{Efficiency of computation on ARGs}
The succinct tree sequence data structure (usually known as a ``tree sequence''
for brevity, but see later comment on confusion around this point)
is a concrete encoding of a gARG, as discussed in this article.
It was originally developed as part of the \texttt{msprime}
simulator~\cite{kelleher2016efficient} and subsequently ...

>>>>

\section*{Precision of recombination information}
Ancestral recombination graphs are often characterised
as consisting of a complete record of the genealogical history
of a sample. For example,
\cite{rasmussen2014genome} state that an ``ARG provides a record of all
coalescence and recombination events since the divergence of the sequences
under study'' and
according to \cite{deng2021distribution} an ARG
``provides all the information about the genealogical history of a sample,
including the locations of recombination events.'' It is worth
questioning, however, whether such complete and precise information is
realistically available, and in particular whether our
\emph{representation} of genealogical history should require
such precision.

@@

@@

It is helpful to consider the difference between fully
resolved binary trees and those that contain polytomies.

The situation is in fact directly analogous: an ARG that
contains fully resolved recombination information must have
at most parents per node.

@@

@@

To illustrate this critical point, we inferred ARGs for the
the \citet{kreitman1983nucleotide} \emph{Drosophila melanogaster} dataset
(classically used as a benchmark for ARG inference),
using four recent inference methods and show the results in
Fig~\ref{fig-inferred-args}).

@@

% Note that all four methods produce output which can be represented in the
% succinct tree sequence format, and which is consistent with our definition of
% an ARG as a data structure. The ARGs produced by \texttt{KwARG} and
% \texttt{ARGweaver} contain more nodes to record the recombination events
% (corresponding to Figure 4 stage `B'), while the ARGs output by
% \texttt{tsinfer} and \texttt{Relate} being, in essence, simplified (roughly
% corresponding to Figure 4 stages `C' and 'D', respectively).

\section*{Computational efficiency}
The succinct tree sequence data structure (usually known as a ``tree sequence''
for brevity, but see later comment on confusion around this point)
is a concrete encoding of a gARG, as discussed in this article.
It was originally developed as part of the \texttt{msprime}
simulator~\cite{kelleher2016efficient} and subsequently ...
